Blum axioms and nondeterministic computation of functions

### 2015-12-16 paper.tex
paper.tex: Explain the "quality standards" for the surveyed definitions.

>>>>

This section surveys four approaches
for defining nondeterministic computation of functions.
Sections \ref{sec:acceptable-godel-numberings} and~\ref{sec:blum-axioms}
can be understood as ``quality requirements''
for the definitions;
that is, the definitions will need to be translatable as
acceptable Gödel numberings,
and the ``natural'' extension of space and time complexity
must satisfy Blum axioms.
